Classical Mechanics Assignment 5

### 2015-11-04 classical/latex/a5.tex
add

\begin{align*}
  PE_{aug} &= \int_{-a}^{a} \left[-gy\rho \sqrt{1 + x'^2} - \lambda\sqrt{1+x'^2}\right]dx\\
  f(y,y',x) &= -gy\rho \sqrt{1 + x'^2} - \lambda\sqrt{1+x'^2}\\
\end{align*}

@@

\begin{align*}
  \frac{-gy\rho x'}{\sqrt{1 + x'^2}} - \frac{\lambda x'}{\sqrt{1+x'^2}} &= k\\
  \frac{-gy\rho x' - \lambda x'}{\sqrt{1 + x'^2}} &= k\\
\end{align*}

>>>>

\begin{align*}
  PE_{aug} &= \int_{-a}^{a} \left[-gy\rho \sqrt{1 + x'^2} - \lambda\sqrt{1+x'^2}\right]dy\\
  f(x,x',y) &= -gy\rho \sqrt{1 + x'^2} - \lambda\sqrt{1+x'^2}\\
\end{align*}

@@

\begin{align*}
  \frac{-gy\rho x'}{\sqrt{1 + x'^2}} - \frac{\lambda x'}{\sqrt{1+x'^2}} &= k\\
  \frac{-gy\rho x' - \lambda x'}{\sqrt{1 + x'^2}} &= k\\
  \left(g^2y^2\rho^2 + \lambda^2 + 2\lambda gy\rho\right)x'^2 &= k^2\left(1 + x'^2\right)\\
  \left(g^2y^2\rho^2 + \lambda^2 + 2\lambda gy\rho -k^2\right)x'^2 &= k^2\\
  x' &= \sqrt{\frac{k^2}{\left(g^2y^2\rho^2 + \lambda^2 + 2\lambda gy\rho -k^2\right)}}\\
  \int dx &= \int \sqrt{\frac{k^2}{\left(g^2y^2\rho^2 + \lambda^2 + 2\lambda gy\rho -k^2\right)}}dy\\
\end{align*}
